---
title: "W_UP_01"
author: "Rita jarbanda"
date: "fall 2023"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

### Plot boxplots

```{r}
basicCN <- ggplot(mydata,aes(x=position,y=pushups))
```

```{r}
basicCN + geom_boxplot(notch=FALSE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```
I'm looking at the columns in the chart above, the left are in positions, and on the right are the skilled positions.

The height of the skilled box is much higher.

The 25th percentile on the skilled player are higher than the 75th percentile of the line players.

This seems to indicate that skilled position can do more push-ups than line position. 

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
favstats(pushups~position,data=mydata)
```
The average line player can do more push ups than the skill player.

## Inferential Results

```{r}
t.test(pushups~position,data=mydata)
```
The p value of 0.0000009421 is so small that it's very strong evidence against the null hypothesis. 
<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

$H_0$ = There is no difference in push-ups based on positions.
$H_0$ = There is a difference in push-ups based on positions.

With assistence from chatgpt I was able to write R code to create a box plot.

Also, by using numerical-cat tool I was able to perform a T test and a summary of the Data (favstats).

The box in onjuction with the summary and T test show that we can reject the $H_0$ leaving only the $H_0$. 
